High-Dimensional Regularized Discriminant Analysis

### 2013-12-30 reports/paper-hdrda.Rnw
Discussed the purpose of alpha_k. #12

\subsection{Relationship with Friedman's RDA Classifier}

@@

To further improve the estimation of $\bm \Sigma_k$ and to stabilize the inverse
of \eqref{eq:sig-lambda}, \cite{Friedman:1989tm} has proposed the biased
covariance-matrix estimator
\begin{align}
          \widehat{\bm \Sigma}_k(\lambda, \gamma) = (1 - \gamma) \widehat{\bm
            \Sigma}_k(\lambda) + \gamma \frac{\tr\{\widehat{\bm
              \Sigma}_k(\lambda)\}}{p} \bm I_p,\label{eq:sig-rda}
          \end{align}
where $\gamma \in [0, 1]$ is a regularization parameter that controls the
shrinkage of \eqref{eq:sig-rda} towards $\bm I_p$ and is weighted by the average
of the eigenvalues of \eqref{eq:sig-lambda}. Finally, the RDA classifier is
established by substituting \eqref{eq:sig-rda} into
\eqref{eq:qda}.\footnote{TODO: Discuss $\alpha_k \equiv 1-\gamma$, etc.}

>>>>

\subsection{Relationship with Other Classifiers}

The addition of the parameter $\alpha_k$ in \eqref{eq:hdrda-cov} is one of
convenience and allows the flexibility of various covariance-matrix estimators
proposed in the literature. In practice, we generally are not interested in
estimating $\alpha_k$ as it would incorporate $K$ additional tuning parameters
to estimate via cross-validation, which is counterproductive to our goal of
improving the \emph{RDA} classifier's efficiency. By setting $\alpha_k$ to a
predefined constant, the \emph{HDRDA} covariance-matrix estimator includes or
resembles a large family of estimators, some of which we mention below.

\subsubsection{\cite{Friedman:1989tm}}

@@

To further improve the estimation of $\bm \Sigma_k$ and to stabilize the inverse
of \eqref{eq:sig-lambda}, \cite{Friedman:1989tm} has proposed the biased
covariance-matrix estimator
\begin{align}
          \widehat{\bm \Sigma}_k(\lambda, \gamma) = (1 - \gamma) \widehat{\bm
            \Sigma}_k(\lambda) + \gamma \frac{\tr\{\widehat{\bm
              \Sigma}_k(\lambda)\}}{p} \bm I_p,\label{eq:sig-rda}
          \end{align}
where $\gamma \in [0, 1]$ is a regularization parameter that controls the
shrinkage of \eqref{eq:sig-rda} towards $\bm I_p$ and is weighted by the average
of the eigenvalues of \eqref{eq:sig-lambda}. Finally, the RDA classifier is
established by substituting \eqref{eq:sig-rda} into
\eqref{eq:qda}.
